Missing Data: Current Practice in Football Research and Recommendations for Improvement

### 2020-11-06 paper/paper.Rmd

---
title: 'Missing Data: Current Practice in Football Research and Recommendations for Improvement'
bibliography: references.bib
output:
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
authors: David N Borg(1), Robert Nguyen(2), Nicholas J Tierney(3,4)
---

@@

```{r load-targets}
loadd(gs_football)
loadd(gs_mismatches)
loadd(simulated_afl_data)
loadd(gs_football_final_matches)
```

@@

Nicholas J Tierney
Monash University, Department of Econometrics and Business Statistics,
Melbourne, Australia.
Address: 
Email: nicholas.tierney@monash.edu

@@

**Word count**

```{r count-words, message = FALSE, warning = FALSE}
wordcountaddin::text_stats()
```

```{r binom-ci-reporting}
n_screened <- nrow(gs_football_final_matches)
n_shared <- sum(gs_football_final_matches$was_data_shared == 1)

binom_ci_miss_reported <- football_binom_confint(
  gs_football_final_matches, 
  any_missing_data_statement
  ) %>% 
  percent_binom_conf()

# now of the articles that don't mention missingness
gs_football_final_matches_dont_report <- gs_football_final_matches %>% 
  filter(any_missing_data_statement == 0)

n_no_mention_missings <- nrow(gs_football_final_matches_dont_report)

binom_ci_data_shared <- gs_football_final_matches_dont_report %>% 
  football_binom_confint(var = was_data_shared) %>% 
  percent_binom_conf()

```

# Abstract {-}

@@

@@

```{r agreement}

md_reported <- agree_var(gs_football, any_missing_data_statement) %>% 
  percent(scale = 1,
          accuracy = 0.1)

```

@@

Methods that provide multiple imputed values for the outcome, such as multiple imputation, or using a Bayesian framework that generates a distribution of posterior values, can be appropriate for imputed the outcome as they provide some sense of what the uncertainty is. For discussion on imputing the response value, see ... [@refs].

Missing values in the outcome can be dealt with specially for Randomised Control Trials, see - https://doi.org/10.1191%2F1740774504cn032oa.

@@

> Missing values of ZZ were imputed with a linear regression using terms XX.
> Missing values were imputed with the mean values

@@

> *Twenty-five of the 280 values in the dataset (~8.92%) were missing. These were due to faults in GPS tracking as participants ran through sections of track covered by forest, a known issue with some GPS tracking. These speed values were interpolated using a nearest neighbours approach, taking inputs of speed, and altitude. The track was imputed using the known track in the area for those sections.*

@@

# References {-}

# Supplement 1

# Supplement 2

>>>>

---
title: 'Missing Data: Current Practice in Football Research and Recommendations for Improvement'
bibliography: references.bib
output:
  bookdown::pdf_document2:
    toc: no
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
  word_document:
    toc: yes
authors: David N Borg(1), Robert Nguyen(2), Nicholas J Tierney(3,4)
csl: sport-medicine.csl
---

@@

```{r load-targets}
loadd(gs_football)
loadd(gs_mismatches)
loadd(simulated_afl_data)
loadd(gs_football_final_matches)
# need to put these into the plan
loadd(n_screened)
loadd(n_shared)
loadd(binom_ci_miss_reported)
loadd(n_no_mention_missings)
loadd(binom_ci_data_shared)
```

@@

Nicholas J Tierney Monash University, Department of Econometrics and Business Statistics, Melbourne, Australia. Address: Email: [nicholas.tierney\@monash.edu](mailto:nicholas.tierney@monash.edu){.email}

@@

<!-- **Word count** -->

```{r count-words, message = FALSE, warning = FALSE, eval = FALSE}
wordcountaddin::text_stats()
```

# Abstract {.unnumbered}

@@

Missing data are values that should have been observed, but were not. Since the values are unobserved, this can mean the population of interest might not be properly sampled, inducing bias into a study's results. Left undetected or poorly handled, missing data can undermine the validity and accuracy of research results [@Sainani2015; @Nakagawa2008; @Sterne2009]. Data can go missing many ways. For example, accidentally skipping a survey question, equipment failure, or intentionally not recording values. Before analysis, missing data must be handled, with values typically deleted or imputed. There is no universal approach to handling missing data. Contextual factors--such as, the study design and objective, and pattern of missingness--determine how missings should be handled, on a case-by-case basis [@Sainani2015].

@@

```{r agreement}
md_reported <- agree_var(gs_football, any_missing_data_statement) %>% 
  percent(scale = 1,
          accuracy = 0.1)
```

@@

Methods that provide multiple imputed values for the outcome, such as multiple imputation, or using a Bayesian framework that generates a distribution of posterior values, can be appropriate for imputing the outcome as they describe the uncertainty [@Krausky2018]. Missing values in the outcome can be dealt with specially for Randomised Control Trials, see - <https://doi.org/10.1191%2F1740774504cn032oa>.

<!-- For discussion on imputing the response value, see ... [@refs]. -->

@@

> Missing values of ZZ were imputed with a linear regression using terms XX. Missing values were imputed with the mean values

@@

> *Twenty-five of the 280 values in the dataset (\~8.92%) were missing. These were due to faults in GPS tracking as participants ran through sections of track covered by forest, a known issue with some GPS tracking. These speed values were interpolated using a nearest neighbours approach, taking inputs of speed, and altitude. The track was imputed using the known track in the area for those sections.*

@@

# References {.unnumbered}
